My English activity log

### 2019-12-01 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 01/12/2019

author:
  - name: Aurélie Pinchart
date: 11-24-2019
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

>>>>

author:
  - name: Aurélie Pinchart
date: 12-01-2019
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

25/11/2019 : I watched a video about electrochemical gradient https://www.youtube.com/watch?v=Ba02v7eoVWQ.

27/11/2019 : I watched a video about viruses https://www.youtube.com/watch?v=8FqlTslU22s.

29/11/2019 : I watched a video about organic molecules https://www.youtube.com/watch?v=tcmGGGJx9zI.

01/12/2019 : I read the tenth chapter of "The Hobbit".
